Append_smoothed_results

### 2016-12-02 Code/1_Explore_Data_v2.Rmd
generalized code for new make_cod_plot fx

       list.cod.decomp.tables[[i]] <- make_dataset_cod_plot(cod.decomp.table = list.cod.decomp.tables[[i]],
                                                            age.groups = "Ages", 
                                                            cause.of.death = "Cause.of.death")

       list.cod.decomp.tables5[[i]] <- make_dataset_cod_plot(cod.decomp.table = list.cod.decomp.tables5[[i]],
                                                            age.groups = "Ages", 
                                                            cause.of.death = "Cause.of.death")

       list.cod.decomp.tables9[[i]] <- make_dataset_cod_plot(cod.decomp.table = list.cod.decomp.tables9[[i]],
                                                            age.groups = "Ages", 
                                                            cause.of.death = "Cause.of.death") 
    } 
  print(i)
}  
```

>>>>

       list.cod.decomp.tables[[i]] <- make_dataset_cod_plot(cod.decomp.table = list.cod.decomp.tables[[i]],
                                                            age.groups = "Ages", 
                                                            cause.of.death = "Cause.of.death", 
                                                            sign.var = "sign", decomp.var = "C_xi", 
                                                            decomp.var.prop = "C_xi_proportion")

       list.cod.decomp.tables5[[i]] <- make_dataset_cod_plot(cod.decomp.table = list.cod.decomp.tables5[[i]],
                                                            age.groups = "Ages", 
                                                            cause.of.death = "Cause.of.death", 
                                                            sign.var = "sign", decomp.var = "C_xi", 
                                                            decomp.var.prop = "C_xi_proportion")

       list.cod.decomp.tables9[[i]] <- make_dataset_cod_plot(cod.decomp.table = list.cod.decomp.tables9[[i]],
                                                            age.groups = "Ages", 
                                                            cause.of.death = "Cause.of.death", 
                                                            sign.var = "sign", decomp.var = "C_xi", 
                                                            decomp.var.prop = "C_xi_proportion") 
    } 
  print(i)
}  
```

### 2016-12-02 Code/append_smoothed_results.Rmd
generalized code for new make_cod_plot fx

       list.cod.decomp.tables.smoothed[[i]] <- make_dataset_cod_plot(cod.decomp.table = list.cod.decomp.tables.smoothed[[i]],
                                                            age.groups = "Ages", 
                                                            cause.of.death = "Cause.of.death")  
    } 
  print(i)
} 
```

>>>>

       list.cod.decomp.tables.smoothed[[i]] <- make_dataset_cod_plot(cod.decomp.table = list.cod.decomp.tables.smoothed[[i]],
                                                            age.groups = "Ages", 
                                                            cause.of.death = "Cause.of.death",
                                                            sign.var = "sign", decomp.var = "C_xi", 
                                                            decomp.var.prop = "C_xi_proportion")  
    } 
  print(i)
} 
```
